A reproducible journal article with RMarkdown&#58; A  building science template with examples for beginners based on the Elsevier journal format

### 2019-02-15 Paper/Manuscript.Rmd
Fix figure chunk formatting, add set.seed

```{r irisTable}
df %>% 
    sample_n(5) %>%   # select 5 random rows from the dataframe
    select(iris_class, sepal_length, petal_length, petal_length_level) %>%  # show only these columns (in this order)
    gt () %>% #make a table
    tab_header( 
    title = "Example irises", # ...with this title
    subtitle = "Data on five randomly selected irises")

@@

```{r irises, message=FALSE, fig.width =8, fig.height = 4.5, fig.cap = "Petal and sepal lengths from iris dataset" }
ggplot(df, aes(x = petal_length, y = sepal_length, group = iris_class)) + 
  geom_smooth(method=lm, se=FALSE, size = 0.5, linetype = "solid", color = "darkgray") +
  geom_point(aes(color = iris_class, shape = long_sepal), alpha = 0.6, size=3) +
  coord_cartesian(xlim = c(0,9), ylim = c(0,9)) + 
  stat_poly_eq(formula = y~x, 
               aes(color=iris_class, label = paste(..eq.label.., sep = "~~~")), 
               parse = TRUE, label.y = c(2, 2.5, 3), 
               label.x = 7, hjust = 1, size = 3.5) +
  scale_y_continuous(expand=c(0,0),expression(Petal~length ~ (cm))) +
  scale_x_continuous(expand=c(0,0),expression(Sepal~length (cm))) +
  guides(color=guide_legend(title="Class",
                            reverse=T, override.aes = list(shape = 15, size=3)), 
         shape=guide_legend(title="long_sepal")) +
  scale_color_manual (values = cal_palette4)
```

## Violin plot example
Figure \@ref(fig:petalwidths) shows petal widths by iris type.
``` {r petalwidths, message=FALSE, fig.width = 8, fig.height = 4.5, fig.cap = "Iris petal widths by species" }
df %>%
    ggplot() + 
    geom_violin(aes( x = iris_class, y = petal_width, color = iris_class), draw_quantiles = T, trim = F, show.legend = F) +
    geom_boxplot(aes( x = iris_class, y = petal_width, color = iris_class), width = 0.07, show.legend = F)+
    scale_color_manual(values=cal_palette4)

>>>>

```{r irisTable}
# The next calculation involves a random draw. Setting a seed ensures the same pseudo-random selection will be made
# each time this document is re-run with the same seed
# Note that deliberately varying the seed and repeating pseudo-random calculations until you achieve for example  a desired but unlikely result is not ethical research practice ('seed hacking`)
set.seed(42)

df %>% 
    sample_n(5) %>%   # select 5 random rows from the dataframe
    select(iris_class, sepal_length, petal_length, petal_length_level) %>%  # show only these columns (in this order)
    gt () %>% #make a table
    tab_header( 
    title = "Example irises", # ...with this title
    subtitle = "Data on five randomly selected irises")

@@

```{r irises, message=FALSE, fig.width =8, fig.height = 4, fig.align='center', fig.cap = "Petal and sepal lengths from iris dataset" }
ggplot(df, aes(x = petal_length, y = sepal_length, group = iris_class)) + 
  geom_smooth(method=lm, se=FALSE, size = 0.5, linetype = "solid", color = "darkgray") +
  geom_point(aes(color = iris_class, shape = long_sepal), alpha = 0.6, size=3) +
  coord_cartesian(xlim = c(0,9), ylim = c(0,9)) + 
  stat_poly_eq(formula = y~x, 
               aes(color=iris_class, label = paste(..eq.label.., sep = "~~~")), 
               parse = TRUE, label.y = c(2, 2.5, 3), 
               label.x = 7, hjust = 1, size = 3.5) +
  scale_y_continuous(expand=c(0,0),expression(Petal~length ~ (cm))) +
  scale_x_continuous(expand=c(0,0),expression(Sepal~length (cm))) +
  guides(color=guide_legend(title="Class",
                            reverse=T, override.aes = list(shape = 15, size=3)), 
         shape=guide_legend(title="long_sepal")) +
  scale_color_manual (values = cal_palette4)
```

## Violin plot example
Figure \@ref(fig:petalwidths) shows petal widths by iris type.

```{r petalwidths, message=FALSE, fig.width = 5, fig.height = 3, fig.align='center', fig.cap = "Iris petal widths by species" }
df %>%
    ggplot() + 
    geom_violin(aes( x = iris_class, y = petal_width, color = iris_class), draw_quantiles = T, trim = F, show.legend = F) +
    geom_boxplot(aes( x = iris_class, y = petal_width, color = iris_class), width = 0.07, show.legend = F)+
    scale_color_manual(values=cal_palette4) 
```
